SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/problems.tex
eval problems #6

He goes on to explain how linking such terms will help make
that inference, and how partial understanding is common in everyday
life and will also be sufficient in my cases on the Web. The practice
of using inference to find a common understanding is now known as
ontology matching or ontology alignment, and is a very active area of
research.\todo{take some open problems in ontology alignment}

@@

\begin{problem}\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
\todo{ Find the ref by Frank on the economics}
\end{problem}

@@

It is clear that neither the vision presented in
Section~\ref{sec:motivation} nor the more advanced vision presented in
\cite{berners2001semantic} exists as of today. In both cases, Semantic
Web would have to be deployed at a very different scale than what it
is today. If the Semantic Web is sufficiently successful to realise
these visions, it is also likely that it will be very different from
today in terms of data profiles, workloads, etc. Since data profiles
and workloads are important to devise a test to evaluate assertions
about performance, the fundamental problem arises that we currently
test against something that does not exist, and this differs markedly
from the methodology of natural science.

Frank van Harmelen has encouraged a direction that seeks to study laws
of the Semantic Web information universe\footnote{See
  e.g. \url{http://videolectures.net/iswc2011_van_harmelen_universal/}
  and
  \url{http://sssw.org/2015/invited-speakers-tutors/frank-vanharmelen/}}.
If this direction is pursued with success, then it may be possible to
establish laws that can be used to generate data and workloads that
can support realistic experiments even though a future Semantic Web
may be several orders of magnitude larger than that of today.

\begin{problem}\label{prob:lawsfuture}
Establish laws of the Semantic Web information universe that can reasonably be
expected to have validity far beyond the present.
\end{problem}

>>>>

He goes on to explain how linking such terms will help make
that inference, and how partial understanding is common in everyday
life and will also be sufficient in my cases on the Web. The practice
of using inference to find a common understanding is now known as
ontology matching or ontology alignment, and is a very active area of
research. This problem, as well as related problems, such as entity
resolution, are considered orthogonal to the problems in this thesis,
so the below problems are issues that arise from the ideal of an open
decentralised Web.

@@

\begin{problem}\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
\end{problem}

@@

It is clear that neither the vision presented in
Section~\ref{sec:motivation} nor the more advanced vision presented in
\cite{berners2001semantic} exists as of today. In both cases, Semantic
Web would have to be deployed at a very different scale than what it
is today. If the Semantic Web is sufficiently successful to realise
these visions, it is also likely that it will be very different from
today in terms of data profiles, workloads, etc. Since data profiles
and workloads are important to devise a test to evaluate assertions
about performance, the fundamental problem arises that: 
\begin{problem}\label{prob:testingnonexist}
We currently test against something that does not exist and therefore
usage patterns cannot be predicted,
\end{problem}
and this differs markedly from the methodology of natural science.

Frank van Harmelen has encouraged a direction that seeks to study laws
of the Semantic Web information universe\footnote{See
  e.g. \url{http://videolectures.net/iswc2011_van_harmelen_universal/}}.
If this direction is pursued with success, then it may be possible to
establish laws that can be used to generate data and workloads that
can support realistic experiments even though a future Semantic Web
may be several orders of magnitude larger than that of today.

\begin{problem}\label{prob:lawsfuture}
No methodology has been established to find laws of the Semantic Web
information universe that can reasonably be expected to have validity
far beyond the present.
\end{problem}
